HEP Software Foundation Community White Paper Working Group -- Data Analysis and Interpretation

### 2018-04-10 CWP/papers/HSF-CWP-2017-05_analysis/latex/cwp-wg-analysis-interpretation.tex
minor updates to sync repo with what was submitted to arXiv

% Copyright (C) 2017, The HSF Community White Paper authors, licence CC-BY-4.0.

@@

\usepackage[style=numeric-comp,sorting=none]{biblatex}
\addbibresource{../../HSF-CWP-2017-01_roadmap/latex/cwp.bib}
\addbibresource{../../HSF-CWP-2017-01_roadmap/latex/cwp-chapters.bib}

@@

\noindent
\begin{tabular*}{\linewidth}{lc@{\extracolsep{\fill}}r@{\extracolsep{0pt}}}
 & & HSF-CWP-2017-05 \\
 & & March 18, 2018 \\ % use \date or hardwire e.g. December 15, 2017
 & & \\
\end{tabular*}
\vspace{1.0cm}

@@

\author{HEP Software Foundation:}
\author[a]{Lothar Bauerdick}
\author[b]{Riccardo Maria Bianchi}
\author[c]{\\ Brian Bockelman}
\author[d,e]{Nuno Castro}
\author[f]{Kyle Cranmer}
\author[g]{Peter Elmer}
\author[h]{\\ Robert Gardner}
\author[i]{Maria Girone}
\author[a,1]{Oliver Gutsche}
\author[i]{Benedikt Hegner}
\author[j]{\\ Jos\'{e} M. Hern\'{a}ndez}
\author[a]{Bodhitha Jayatilaka}
\author[g]{David Lange}
\author[k,1]{Mark Neubauer}
\author[k]{Daniel S. Katz}
\author[l]{Lukasz Kreczko}
\author[m]{James Letts}
\author[n]{Shawn McKee}
\author[o]{\\ Christoph Paus}
\author[a]{Kevin Pedro}
\author[g]{Jim Pivarski}
\author[p]{Eduardo Rodrigues}
\author[l]{Tai Sakuma}
\author[a]{Elizabeth Sexton-Kennedy}
\author[p]{Michael D. Sokoloff}
\author[q]{Carl Vuosalo}
\author[m]{\\ Frank W\"{u}rthwein}
\author[r]{Gordon Watts}

\affiliation[a]{Fermi National Accelerator Laboratory, Batavia, Illinois USA}
\affiliation[b]{University of Pittsburgh, Pittsburgh, Pennsylvania, USA}
\affiliation[c]{University of Nebraska-Lincoln, Lincoln, Nebraska, USA}
\affiliation[d]{Laboratório de Instrumentação e Física Experimental de Partículas, Lisbon, Portugal}
\affiliation[e]{University of Minho, Braga, Portugal}
\affiliation[f]{New York University, New York, New York, USA}
\affiliation[g]{Princeton University, Princeton, New Jersey, USA}
\affiliation[h]{University of Chicago, Chicago, Illinois, USA}
\affiliation[i]{CERN, Geneva, Switzerland}
\affiliation[j]{Centro de Investigaciones Energéticas, Medioambientales y Tecnológicas, Madrid, Spain}
\affiliation[k]{University of Illinois at Urbana-Champaign, Urbana, Illinois USA}
\affiliation[l]{University of Bristol, Bristol, UK}
\affiliation[m]{University of California at San Diego, La Jolla, California, USA}
\affiliation[n]{University of Michigan, Ann Arbor, Michigan, USA}
\affiliation[o]{Massachusetts Institute of Technology, Cambridge, Massachusetts, USA}
\affiliation[p]{University of Cincinnati, Cincinnati, Ohio, USA}
\affiliation[q]{University of Wisconsin-Madison, Madison, Wisconsin, USA}
\affiliation[r]{University of Washington, Seattle, Washington, USA}
\affiliation[1]{Paper Editor}

%\affiliation[c]{Laboratório de Instrumentação e Física Experimental de Partículas, Lisbon, Portugal and University of Minho, Braga, Portugal, Supported by FCT-Portugal, IF/00050/2013/CP1172/CT0002}
%\affiliation[g]{Fermi National Accelerator Laboratory, Batavia, Illinois USA, Supported by the US-DOE, DE-AC02-07CH11359}
%\affiliation[h]{Centro de Investigaciones Energéticas, Medioambientales y Tecnológicas (CIEMAT), Madrid, Spain, Supported by ES-MINECO, FPA2016-80994-c2-1-R and MDM-2015-0509}
%\affiliation[i]{University of Illinois at Urbana-Champaign, Urbana, Illinois USA, Supported by the US-DOE, DE-SC0018098 and US-NSF ACI-1558233}
%\affiliation[m]{University of Michigan, Supported by the US-DOE, DE-SC0007859 and US-NSF, 76749/1136652/2}
%\affiliation[o]{University of Cincinnati, Supported by the US-NSF, ACI-1450319}
%\affiliation[p]{University of Cincinnati, Supported by the US-NSF, ACI-1558219}

>>>>

% Copyright (C) 2018, The HSF Community White Paper authors, licence CC-BY-4.0.

@@

\usepackage[style=numeric-comp,sorting=none]{biblatex}
\addbibresource{cwp.bib}
\addbibresource{cwp-chapters.bib}

@@

\noindent
\begin{tabular*}{\linewidth}{lc@{\extracolsep{\fill}}r@{\extracolsep{0pt}}}
 & & HSF-CWP-2017-05 \\
 & & March 25, 2018 \\ % use \date or hardwire e.g. December 15, 2017
 & & \\
\end{tabular*}
\vspace{1.0cm}

@@

\author{HEP Software Foundation:}
\author[a]{Lothar Bauerdick}
\author[b]{Riccardo Maria Bianchi}
\author[c]{\\ Brian Bockelman}
\author[d,e]{Nuno Castro}
\author[f]{Kyle Cranmer}
\author[g]{Peter Elmer}
\author[h]{\\ Robert Gardner}
\author[i]{Maria Girone}
\author[a,1]{Oliver Gutsche}
\author[i]{Benedikt Hegner}
\author[j]{\\ Jos\'{e} M. Hern\'{a}ndez}
\author[a]{Bodhitha Jayatilaka}
\author[g]{David Lange}
\author[k,1]{Mark S. Neubauer}
\author[k]{Daniel S. Katz}
\author[l]{Lukasz Kreczko}
\author[m]{James Letts}
\author[n]{Shawn McKee}
\author[o]{\\ Christoph Paus}
\author[a]{Kevin Pedro}
\author[g]{Jim Pivarski}
\author[p]{Martin Ritter}
\author[q]{Eduardo Rodrigues}
\author[l]{Tai Sakuma}
\author[a]{Elizabeth Sexton-Kennedy}
\author[p]{Michael D. Sokoloff}
\author[r]{\\ Carl Vuosalo}
\author[m]{Frank W\"{u}rthwein}
\author[s]{Gordon Watts}

\affiliation[a]{Fermi National Accelerator Laboratory, Batavia, Illinois USA}
\affiliation[b]{University of Pittsburgh, Pittsburgh, Pennsylvania, USA}
\affiliation[c]{University of Nebraska-Lincoln, Lincoln, Nebraska, USA}
\affiliation[d]{Laboratório de Instrumentação e Física Experimental de Partículas, Lisbon, Portugal}
\affiliation[e]{University of Minho, Braga, Portugal}
\affiliation[f]{New York University, New York, New York, USA}
\affiliation[g]{Princeton University, Princeton, New Jersey, USA}
\affiliation[h]{University of Chicago, Chicago, Illinois, USA}
\affiliation[i]{CERN, Geneva, Switzerland}
\affiliation[j]{Centro de Investigaciones Energéticas, Medioambientales y Tecnológicas, Madrid, Spain}
\affiliation[k]{University of Illinois at Urbana-Champaign, Urbana, Illinois USA}
\affiliation[l]{University of Bristol, Bristol, UK}
\affiliation[m]{University of California at San Diego, La Jolla, California, USA}
\affiliation[n]{University of Michigan, Ann Arbor, Michigan, USA}
\affiliation[o]{Massachusetts Institute of Technology, Cambridge, Massachusetts, USA}
\affiliation[p]{Fakultät für Physik, Ludwig-Maximilians-Universität München, München, Germany}
\affiliation[q]{University of Cincinnati, Cincinnati, Ohio, USA}
\affiliation[r]{University of Wisconsin-Madison, Madison, Wisconsin, USA}
\affiliation[s]{University of Washington, Seattle, Washington, USA}
\affiliation[1]{Paper Editor}
